--- 
title: "R语言与生物统计（畜牧兽医篇）"
author: "李任峰"
date: "`r Sys.Date()`"
output:
  pdf_document: pdf_document2
  html_document:
    df_print: paged
documentclass: book
bibliography:
- book.bib
- packages.bib
description: |
  This is a minimal example of using the bookdown package to write a book.
  set in the _output.yml file.
  The HTML output format for this example is bookdown::gitbook,
link-citations: yes
github-repo: "rstudio/bookdown-demo"
site: bookdown::bookdown_site
---

# 序言{-}


<!--chapter:end:index.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# Footnotes and citations 

## Footnotes

Footnotes are put inside the square brackets after a caret `^[]`. Like this one ^[This is a footnote.]. 

## Citations

Reference items in your bibliography file(s) using `@key`.

For example, we are using the **bookdown** package [@R-bookdown] (check out the last code chunk in index.Rmd to see how this citation key was added) in this sample book, which was built on top of R Markdown and **knitr** [@xie2015] (this citation was added manually in an external file book.bib). 
Note that the `.bib` files need to be listed in the index.Rmd with the YAML `bibliography` key.


The RStudio Visual Markdown Editor can also make it easier to insert citations: <https://rstudio.github.io/visual-markdown-editing/#/citations>

<!--chapter:end:04-citations.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:07-references.Rmd-->

---
output:
  pdf_document:
    toc: yes
  word_document:
    toc: yes
  html_document:
    toc: yes
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
---

# 第1章 R语言基础{-} 

All chapters start with a first-level heading followed by your chapter title, like the line above. There should be only one first-level heading (`#`) per .Rmd file.

## 1.1 软件安装{-}

All chapter sections start with a second-level (`##`) or higher heading followed by your section title, like the sections above and below here. You can have as many as you want within a chapter.

### 1.1.1 R的安装{-}

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the shorter `{-}` at the end of the heading, like in this section.
```{r}
a<- c(1,2,3)
b <- c(8,9,10)
plot(a,b)
```

### 1.1.2 Rstudio的安装{-}

### 1.1.3 R包的安装{-}

## 1.2 数据类型{-}

## 1.3 输入数据{-}



<!--chapter:end:第1章-R语言基础.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# 第2章 数据管理{-}

Cross-references make it easier for your readers to find and link to elements in your book.

## 2.1 缺失值处理{-}

There are two steps to cross-reference any heading:

1. Label the heading: `# Hello world {#nice-label}`. 
    - Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    - To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.

1. Next, reference the labeled heading anywhere in the text using `\@ref(nice-label)`; for example, please see Chapter \@ref(cross). 
    - If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#cross).

## 2.2 数据类型转换{-}

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
 
## 2.3 数据整理{-}

<!--chapter:end:第2章-数据管理.Rmd-->

---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
# 第3章 R与统计{-}

You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.

## 3.1 R中的基本统计函数{-}
```{r}
load("C:/Users/liren/Desktop/R学习/在学/参考兽医统计教材/数据集/data_rdata/data_rdata/Data_Set_1.rdata")#加载数据
head(data_set_1) #查看数据
str(data_set_1) #查看数据格式
table(data_set_1) #查看数据分布频率
summary(data_set_1)
```



## 3.2 回归分析{-}




<!--chapter:end:第3章-R与统计.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# 第4章 R语言绘图{-}

## 4.1 基本绘图{-}

Footnotes are put inside the square brackets after a caret `^[]`. Like this one ^[This is a footnote.]. 

## 4.2 高级绘图{-}

Reference items in your bibliography file(s) using `@key`.

For example, we are using the **bookdown** package [@R-bookdown] (check out the last code chunk in index.Rmd to see how this citation key was added) in this sample book, which was built on top of R Markdown and **knitr** [@xie2015] (this citation was added manually in an external file book.bib). 
Note that the `.bib` files need to be listed in the index.Rmd with the YAML `bibliography` key.


The RStudio Visual Markdown Editor can also make it easier to insert citations: <https://rstudio.github.io/visual-markdown-editing/#/citations>

<!--chapter:end:第4章-R语言绘图.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# 第5章 R语言与机器学习{-}

## 5.1 回归分析{-}

Here is an equation.

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

You may refer to using `\@ref(eq:binom)`, like see Equation \@ref(eq:binom).


## 5.2 聚类分析{-}

Labeled theorems can be referenced in text using `\@ref(thm:tri)`, for example, check out this smart theorem \@ref(thm:tri).

::: {.theorem #tri}
For a right triangle, if $c$ denotes the *length* of the hypotenuse
and $a$ and $b$ denote the lengths of the **other** two sides, we have
$$a^2 + b^2 = c^2$$
:::

Read more here <https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html>.

## 5.3 贝叶斯分析{-}


The R Markdown Cookbook provides more help on how to use custom blocks to design your own callouts: https://bookdown.org/yihui/rmarkdown-cookbook/custom-blocks.html

<!--chapter:end:第5章-R语言与机器学习.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# 第6章 R与智能化编程{-}

## 6.1 Publishing{-}

HTML books can be published online, see: https://bookdown.org/yihui/bookdown/publishing.html

## 6.2 404 pages{-}

By default, users will be directed to a 404 page if they try to access a webpage that cannot be found. If you'd like to customize your 404 page instead of using the default, you may add either a `_404.Rmd` or `_404.md` file to your project root and use code and/or Markdown syntax.


Bookdown HTML books will provide HTML metadata for social sharing on platforms like Twitter, Facebook, and LinkedIn, using information you provide in the `index.Rmd` YAML. To setup, set the `url` for your book and the path to your `cover-image` file. Your book's `title` and `description` are also used.



This `gitbook` uses the same social sharing data across all chapters in your book- all links shared will look the same.

Specify your book's source repository on GitHub using the `edit` key under the configuration options in the `_output.yml` file, which allows users to suggest an edit by linking to a chapter's source file. 

Read more about the features of this output format here:

https://pkgs.rstudio.com/bookdown/reference/gitbook.html

Or use:

```{r eval=FALSE}
?bookdown::gitbook
```



<!--chapter:end:第6章-R与智能化编程.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# 第7章 R在畜牧兽医领域的应用{-}

## 7.1 Publishing{-}

HTML books can be published online, see: https://bookdown.org/yihui/bookdown/publishing.html

## 7.2 404 pages{-}

By default, users will be directed to a 404 page if they try to access a webpage that cannot be found. If you'd like to customize your 404 page instead of using the default, you may add either a `_404.Rmd` or `_404.md` file to your project root and use code and/or Markdown syntax.


Bookdown HTML books will provide HTML metadata for social sharing on platforms like Twitter, Facebook, and LinkedIn, using information you provide in the `index.Rmd` YAML. To setup, set the `url` for your book and the path to your `cover-image` file. Your book's `title` and `description` are also used.



This `gitbook` uses the same social sharing data across all chapters in your book- all links shared will look the same.

Specify your book's source repository on GitHub using the `edit` key under the configuration options in the `_output.yml` file, which allows users to suggest an edit by linking to a chapter's source file. 

Read more about the features of this output format here:

https://pkgs.rstudio.com/bookdown/reference/gitbook.html

Or use:

```{r eval=FALSE}
?bookdown::gitbook
```



<!--chapter:end:第7章-R语言在畜牧兽医领域的应用.Rmd-->

