---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
# 第3章 R与统计{-}

You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.

## 3.1 R中的基本统计函数{-}
```{r}
load("C:/Users/liren/Desktop/R学习/在学/参考兽医统计教材/数据集/data_rdata/data_rdata/Data_Set_1.rdata")#加载数据
head(data_set_1) #查看数据前6行
str(data_set_1) #查看数据格式
table(data_set_1) #查看数据分布频率
summary(data_set_1)
```
## 3.2 基本统计函数
```{r}
attach(data_set_1) #当采用attach()时可不用$选取变量（注意：该方法容易造成变量操作混乱，一般不建议）。
summary(data_set_1) #summary()生成最大值、最小值、平均值、中位数、第1、3分位数等信息。另外，该函数可对矩阵、数据框、因子等多种类型的数据进行总结。
table(data_set_1) #用table()函数创建频率表，生成每个元素（或因子）出现的频数。
x <- table(data_set_1)
names(x)[which(x==max(x))]#查询出现频率最高的元素
min(data_set_1) #查看最小值
max(data_set_1) #查看最大值
y <- range(data_set_1) #查看最大与最小值
diff(y) #查看最大与最小值之间的差值
length(data_set_1)
length(data_set_1$Threshold) #length()函数查看数据集中变量个数（数据容量）
quantile(data_set_1$Threshold)
quantile(data_set_1$Threshold,0.25)
quantile(data_set_1$Threshold,0.75)
IQR(data_set_1$Threshold) #计算四分位距（IQR），它是Q3和Q1之间的差值，即IQR = Q3 - Q1

mean(Threshold) #平均值（前面需先用attach()函数加载数据）
median(Threshold) #中位数
var(Threshold) #求方差
sd(Threshold) #求标准差




```



## 3.3 回归分析{-}



